%\documentclass[draftcls,onecolumn]{IEEEtran}
\documentclass[final,onecolumn]{IEEEtran}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                              %
%                                   PREAMBLE                                   %
%                                                                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INCLUDING THE PREAMBLE
\input{../Preamble}
\usepackage{standalone}
\usepackage{siunitx}
%\graphicspath{{./images/}{./}}
%\DeclareGraphicsExtensions{.pdf, .jpeg, .png, .jpg}
% TO COMPILE: lmake
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                              %
%                               START OF DOCUMENT                              %
%                                                                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

% Cover Page
\title{Moderation of Neutron Sources with HDPE}
\author{Matthew J. Urffer}
\date{Febuary 20, 2013}

\maketitle
\begin{abstract}
The moderation of neutrons by high density polyethylene (HDPE) is investigated as a function of source energy and thickness of HDPE.
MCNPX was used to simulate the neutronics for a point neutron source, as well as a \iso[252]{Cf} source for thickness ranging from \SI{0.5}{\centi\meter} to \SI{32}{\centi\meter}.
A series of curves were constructed in order to present this data plotting the thermal fraction of the spectra versus moderator thickness.
It is observed for neutrons with an energy below 1 keV less than \SI{2}{\centi\meter} of HDPE moderator are needed in order to have a thermal fraction greater than 10 \%.
For 1 MeV neutrons about \SI{4}{\centi\meter} of moderator are needed, while for the \iso[252]{Cf} source spectra about \SI{8}{\centi\meter} of moderator are needed in order to thermalize the spectra to above 10\%.
\end{abstract}

\IEEEpeerreviewmaketitle

% Tables of Contents, Figures, Tables
\tableofcontents
\listoftodos
\listoffigures
\lstlistoflistings

\section{Introduction}
Understanding the moderation of neutrons is essential for neutron detector design.
Many of the neutron detection reactions have a significantly larger (by orders of magnitudes) probability of occurrence if the neutrons are thermal.
For example, \iso[6]{Li} has a total neutron absorbtion cross section of \SI{5.4}{\barn} at \SI{1}{\kilo\electronvolt} which increase to \SI{150}{\barn} at \SI{1}{\electronvolt}.
Thus, great effort is taken to moderate the neutron spectra in order to increase the probability of a desired reaction occuring.
High density polyethylene (HDPE) is a well known neutron moderator with a density ranging from \SI{0.93}{\gram\per\cubic\centi\meter} to \SI{0.97}{\gram\per\cubic\centi\meter}.
Polyethylene,$~\left (C_2 H_4\right )_n H_2~$, has four hydrogen atoms per repeating unit making it an ideal neutron moderator because each neutron can lose almost all of it's energy upon an elastic collision with a hydrogen atom.
HDPE is also stable at room temperature, non-toxic, and has enough structural integrity that one can build with it.

This work will focus on the moderation of two types of neutron sources; a mono energetic point source of various energies and a \iso[252]{Cf} source.
For both sources the thickness of HDPE encasing the source is varied, and the fraction of thermal neutrons is calculated.
This paper is organized into the following sections.  Section \ref{sec:Methods} will outline the geometry used for the MCNPX simulation, as well as an in depth explanation of how the fraction of thermal neutrons was calculated.
Section ~\ref{sec:Results} will outline the results, while section ~\ref{sec:Conclusions} will summarize the work.

\input{HDPEMethods}
\input{HDPEResults}

\section{Conclusions}
\label{sec:Conclusions}
The fraction of the neutron spectra that had energies below 0.5 eV was calculated for a variety of points sources and HDPE moderator thickness.
In addition, the thermal fraction was calculated for different thickness of HDPE moderator surrounding a \iso[252]{Cf} source encased in 0.5 cm of lead.
It was found that 2 cm in sufficient to have over 10\% of neutrons with an initial energy of 1 keV to have an energy below 0.5 eV.
For the more energetic \iso[252]{Cf} source (most probable energy of 0.7 MeV and an average energy of 2.1 MeV) the thermal fraction was above 10\% with a moderator thickness slightly less than 8 cm.

% Bibliography
\bibliography{./Zotero}

\newpage
\appendix
\input{HDPEListings}
%\include{DTDDSheilding}

\end{document}

